Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-16 Paper/paper.tex
Updated FOTN figure

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move online and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 million in 2005 to 3.578 million
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S.\ were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\caption{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017)}\label{fig:fotn2017}
\end{figure}

>>>>

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move online and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 million in 2005 to 3.578 million
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S.\ were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Also, other forms of Internet
tampering such as code injection~\cite{badtraffic,191996} have been observed within the
Internet's backbone. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\caption{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017). 
	Green nations are free, yellow are mostly free, and blue are not free according to FOTN.}\label{fig:fotn2017}
\end{figure}
